D3064R0: Bringing the Laws of Physics to Bear on the OOTA Problem

### 2024-01-11 ootavacuous.tex
Explicitly say how C++ accounts for some control dependencies
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{itemize}
\item	Loads that do not affect observable behavior can be omitted,
	along with any computations based on their return values.
\item	Given a pair of loads from the same object that can be
	reordered to be adjacent to each other, if one of the pair is a
	relaxed load, it can be omitted, with uses of the omitted load
	instead using the value returned by the surviving load.
	This is termed \emph{load fusing}.
\item	Given a pair of stores to the same object that can be reordered
	to be adjacent to each other, if the first of the pair is a
	relaxed store, it can be omitted.
	This is termed \emph{store fusing}.
\item	Suppose the source code contains a pair of non-volatile atomic
	loads from objects that are adjacent in memory.
	Suppose further that these loads can be reordered to be adjacent
	to each other, and that the last of the two is a relaxed load.
	Then this pair of loads can be replaced with a single load
	from both objects using the first load's memory order.
	This is termed \emph{load consolidation}.
\item	Suppose the source code contains a pair of non-volatile atomic
	stores to objects that are adjacent in memory.
	Suppose further that these stores can be reordered to be adjacent
	to each other, and that the first of the two is a relaxed load.
	Then this pair of loads can be replaced with a single store
	to both objects using the last store's memory order.
	This is termed \emph{store consolidation}.
\item	If an expression can be proven to always result in a constant,
	that constant can be substituted for that expression.
	Note well that combining this with specialization optimizations
	can convert address and data dependencies to weaker control
	dependencies.
	Address and data dependencies order later loads and stores,
	and control dependencies order only later stores.\footnote{
		Yes, yes, the C++ standard does not mention address or
		data dependencies, and mandates control dependencies
		only indirectly.
		Such dependencies nevertheless still exist.}
\end{itemize}

@@

\subsection{But What About Multi-Thread Optimizations?}
\label{sec:But What About Multi-Thread Optimizations?}

>>>>

\begin{itemize}
\item	Loads that do not affect observable behavior can be omitted,
	along with any computations based on their return values.
\item	Given a pair of loads from the same object that can be
	reordered to be adjacent to each other, if one of the pair is a
	relaxed load, it can be omitted, with uses of the omitted load
	instead using the value returned by the surviving load.
	This is termed \emph{load fusing}.
\item	Given a pair of stores to the same object that can be reordered
	to be adjacent to each other, if the first of the pair is a
	relaxed store, it can be omitted.
	This is termed \emph{store fusing}.
\item	Suppose the source code contains a pair of non-volatile atomic
	loads from objects that are adjacent in memory.
	Suppose further that these loads can be reordered to be adjacent
	to each other, and that the last of the two is a relaxed load.
	Then this pair of loads can be replaced with a single load
	from both objects using the first load's memory order.
	This is termed \emph{load consolidation}.
\item	Suppose the source code contains a pair of non-volatile atomic
	stores to objects that are adjacent in memory.
	Suppose further that these stores can be reordered to be adjacent
	to each other, and that the first of the two is a relaxed load.
	Then this pair of loads can be replaced with a single store
	to both objects using the last store's memory order.
	This is termed \emph{store consolidation}.
\item	If an expression can be proven to always result in a constant,
	that constant can be substituted for that expression.
	Note well that combining this with specialization optimizations
	can convert address and data dependencies to weaker control
	dependencies.
	Address and data dependencies order later loads and stores,
	and control dependencies order only later stores.\footnote{
		Yes, yes, the C++ standard does not mention address or
		data dependencies, and mandates control dependencies
		only indirectly (via the prohibition against introducing
		data races).
		Such dependencies nevertheless still exist.}
\end{itemize}

@@

\subsection{But What About Multi-Threaded Optimizations?}
\label{sec:But What About Multi-Threaded Optimizations?}
